Forecasting the old-age dependency ratio to determine the best pension age

### 2019-01-13 PensionAge.Rmd
Draft_13/Jan/2019

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = TRUE)
# Make sure you have the latest version of rmarkdown and bookdown
# devtools::install_github("rstudio/rmarkdown")
# devtools::install_github("rstudio/bookdown")
# And the latest versions of Our packages
# devtools::install_github("robjhyndman/forecast")
# devtools::install_github("robjhyndman/demography")
# devtools::install_github("robjhyndman/addb")
library(demography)
library(addb)
library(ggplot2)
source("functions-v4.R")
```

@@

```{r changespension, echo=FALSE, fig.cap="Government's adjustments on pension age scheme.", fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
year <- 2065 - 2007
proposed <- ts(pmin(
  70,
  c(rep(65, 2017 - 2008), 65 + cumsum(rep(c(0.5, 0), 55)))
)[1:50],
start = 2008
)
approved <- pmin(proposed, 67)
current <- pmin(proposed, 65)
cols <- c(current = "#1b9e77", approved = "#d95f02", proposed = "#7570b3")
ggplot() +
  forecast::autolayer(proposed, series = "proposed") +
  forecast::autolayer(approved, series = "approved") +
  forecast::autolayer(current, series = "current") +
  xlab("Year") + ylab("Age of retirement") +
  scale_color_manual(
    values = cols, name = " ",
    breaks = c("current", "approved", "proposed"),
    labels = c("Pension age at 65", "Approved change", "Proposed further change")
  )
```

@@

The model proposed by @LC92 is as follows:
\begin{equation}
  \ln(m_{x,t})=a_x+b_xk_t+\epsilon_{x,t}
\end{equation}
where $m_{x,t}$ is the central death rate\footnote{The central death rate is properly defined in Section~\ref{sec:data}} for age $x$ in year $t$. This model involves fitting a matrix of log central rates with sets of age-specific constants, {$a_x$} and {$b_x$}, and a time-varying index $k_t$. $b_x$ is a set of parameters that tell us the rate at which each age responds to changes in $k_t$. $k_t$ measures the general level of the log death rates; $a_x$ is the general pattern across age of the log mortality rate and $\epsilon_{x,t}$ is an error term with zero mean and constant variance, reflecting the randomness that can't be captured by the model.

The model is under-determined in terms of estimation of parameters. For example, if the vector $a,b,k$ is one solution, then for any scalar $c, a-bc, b, k+bc$ also must be one solution. Therefore, Lee and Carter (1992) impose the following constraints:
\begin{equation}
  \sum_{t=1}^{n}k_t=0, \sum_{x=x_1}^{x_m}b_x=1
\end{equation}
Also, we normally seek the least squares solution when estimating parameters. However, in this case, the model cannot be estimated using simple regression methods because there is no regressor on the right side of the equation. @LC92 choose a singular value decomposition (SVD) method to undertake principal component analysis (PCA), and hence find the least squares solution. It has been shown that applying SVD method to a matrix of the logarithms of the rates after subtracting the average over time of the log age-specific rates can find the least square solution (Good, 1969). Therefore, the estimations of $b_x$ and $k_t$ are the first principal component and scores of $\ln(m_{x,t})-a_x$ (i.e., $b_x=\bm{z_1}$ and $k_t=\bm{u_1}'$  when $\bm{X}=\ln(m_{x,t})-a_x$). However, the empirical results suggest that the resulting fitted number of deaths are biased estimates of actual number of deaths because of the $\ln$ transformation. To overcome this problem, the LC method adjusts $k_t$ such that for each year, the implied number of deaths will be equal to the actual number of deaths. The adjusted $k_t$ is then extrapolated using random walk with drift models, which is equivalent to ARIMA ($0,1,0$) model with $c\neq0$.

### Hyndman-Ullah Method

@@

The model proposed by @HU07 is as follows:
\begin{align}
  y_t(x) & = s_t(x) + \sigma_t(x)\epsilon_{t,x}\label{eq:HU_1}\\
  s_t(x) & = \mu(x) + \sum_{j=1}^{J}\beta_{t,j}\phi_j(x) + e_t(x)\label{eq:HU_2}
\end{align}
Equation \eqref{eq:HU_1} describes the smoothing process. $y_t(x)$ is the observed data in year $t$ and age $x$, and $s_t(x)$ is the smoothed function of $y_t(x)$, estimated by constrained weighted penalized regression splines [@BHT14]. $\sigma_t(x)$ allows the variance to be a function of time and age; and $\epsilon_{t,x}$ are independent identical distributed standard normal error terms. Equation \eqref{eq:HU_2} has a similar structure to the LC method, except that it incorporates more than one principal component and score. It describes the dynamics of $s_t(x)$ over time. The $\beta_{t,j}$ for every $j$ and $\mu(x)$ are sets of age-specific constants, and $\phi_j(x)$ for every $j$ is a time-varying index. The $e_t(x)$ is the model error, which is the residual function with mean zero and no serial correlation. The $\mu(x)$ is estimated by the average of $s_t(x)$ across years, which measures the general shape of the observed data $y_t(x)$. The estimates of $\phi_j(x)$ and $\beta_{t,j}$ are the $j$th principal component and scores of $s_t(x)-\mu(x)$ respectively. In other words, we take singular value decomposition of $s_t(x)-\mu(x)$, then \eqref{eq:HU_2} now becomes
\begin{equation*}
  s_t(x)-\mu(x) = \phi_1(x)\beta_{t,1}+\phi_2(x)\beta_{t,2}+\dots+\phi_k(x)\beta_{t,k}
\end{equation*}
We chose $J$ in a way that we believe the majority of information for $s_t(x)-\mu(x)$ has been captured by the first $J$ components.

In terms of forecasting, by conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}$ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of log rate $y_{n+h}(x)$ can be acquired by:
\begin{equation}
  \widehat{y}_{n+h\mid n}(x)=\widehat{s}_{n+h\mid n}(x) = \text{E}[\widehat{s}_{n+h\mid n}(x)\mid \bm{I, B}] = \widehat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\widehat{\beta}_{n+h\mid n,j}
\end{equation}
where $\widehat{\beta}_{n+h\mid n,j}$ denotes the $h$-step-ahead forecast of $\beta_{n+h\mid n,j}$. Because of the time-varying property of $\left\{\beta_{t,j}\right\}$, it controls the dynamics of the process. For every component series $\left\{\beta_{t,j}\right\}$, we fit them with an ARIMA$(p_j,d_j,q_j)$ process, where $p_j,d_j,q_j$ are determined by minimizing the Akaike Information Criterion (Booth, Hyndman \& Tickle, 2014). The fitted process is given as follows:
\begin{equation*}
  (1-\phi_1B-\dots-\phi_{p_j}B^{p_j})(1-B)^{d_j}\beta_{t,j}=c+(1+\theta_1B+\dots+\theta_{q_j}B^{q_j})e_t, \quad ~\forall j=1,2,\dots,J,
\end{equation*}
where the parameters are estimated using maximum likelihood estimation.

@@

We use the same notation and similar procedures to construct data as in @HB08, because the fundamental model for forecasting population for this study is the @HU07 method. The data used to construct population age structure included: age- and gender-specific birth and death numbers of each calendar year, age- and gender-specific population members on 1\ January of each year, and age- and gender-specific exposures to risk (i.e., population of age $x$ at 30 June) for each year. The notations are as follows:
\begin{align*}
  B_t(x) &= \text{Births in calendar year $t$ to females of age $x$}\\
  D_t(x) &= \text{Deaths in calendar year $t$ of persons of age $x$}\\
  P_t(x) &= \text{Population of age $x$ at 1 January of year $t$}\\
  E_t(x) &= \text{Population of age $x$ exposed to risk at 30 June of year $t$}\\
\end{align*}
where $x$ denotes age and $x=0,1,2,\dots,m^+$. $m^+$ is the open-ended upper age group, which is 100 in this study. $t$ denotes year and $t=1,2,\dots,n$, where $n$ is the horizon of historical data used. Therefore, all of those data points can be recorded in an $m\times n$ matrix.  The super-scripts $M$ and $F$ denote male and female respectively.

We can obtain historical mortality rates $m_t(x)$ (also called central death rates) and fertility rates $f_t(x)$ as follows:
\begin{align*}
  m_t(x) & = \frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year t}\\
  f_t(x) & = \frac{B_t(x)}{E^F_t(x)}=\text{age-specific fertility rates in calendar year t}
\end{align*}

In addition, the net migration\footnote{Net migration is the difference between immigration and emigration in a certain area during a specified time frame} (denoted $G$) is estimated using a demographic growth-balance equation, which is an equation to summarize the relationship between population change and three factors: net migration, births and deaths. The equation is expressed as: \todo{Please define $p$ and $^+$}
\begin{align*}
  G_t(x,x+1)     & =P_{t+1}(x+1)-P_t(x)+D_t(x,x+1)\text{~for~} x=0,1,2,\dots,p-2,\\
  G_t(p-1^+,p^+) & =P_{t+1}(p^+)-P_t(p^+)-P_t(p-1)+D_t(p-1^+,p^+)\\
  G_t(B,0)       & =P_{t+1}(0)-B_t+D_t(B,0)
\end{align*}
where $G_t(x,x+1)$ refers to net migration in calendar year $t$ of persons aged $x$ at beginning of year $t$, $G_t(p-1^+,p)$ refers to migration in calendar year $t$ of persons aged $p-1$ and older at beginning of year $t$, and $G_t(B,0)$ refers to deaths in calendar year $t$ of births during year $t$; and similarly for deaths, $D_t(x,x+1), D_t(p-1^+,p^+), D_t(B,0)$. The deaths are estimated using the standard life table approach of population projection. It should be noted that the estimated net migration includes errors in data recording.

Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0-99 and 100+ have been sourced from the @HMD for 1921--2014. The start-year population for 2015 is also used to estimate net migration. Data for age-specific annual fertility rates by single years of age for 15-49 over the period 1950-2014 was obtained from the @ABS12. Even though annual mortality rates are available from 1921 to 2009, only data collected after 1950 is used for two reasons. First, the period between 1921-1950 has very different mortality patterns from later years because of wars and epidemics [@HB08]. Since the model for this study is valid under the assumption that extrapolative methods can be used, it seemed best to delete the less relevant data, which might influence estimations of parameters if we include them. Secondly, fertility rates are only available from 1950, so the mortality rate was cut to fit the same period. \todo{Han has updated the data period.}

@@

In this study, three steps were taken to simulate OADR associated with a specific pension age scheme. A stochastic functional model was applied to five components of population change: female mortality rates, male mortality rates, female net migration, male net migration and fertility rates to simulate these five components over the prediction horizon (which is 50 years in this study). age- and gender-specific population paths over the prediction horizon were simulated using the demographic growth-balance equation. The Monte Carlo simulation method was used consistently in this research. Finally, calculation of OADR associated with a specific pension age scheme was performed by applying the OADR formula. Even though the process seems complicated, it is relatively resy to implement using \textit{R}. The detailed explanation of each step is as follows. The corresponding R code is attached in Appendix B. \todo{There is no appendix, Han recommends to put the R code as a supplement}

@@

The main procedure for forecasting the population age structure follows @HB08, except that the data is updated, and we incorporate the product-ratio method [@HBY13] to improve the accuracy of the forecast. The @HU07 model, introduced in section 2.3.2, is applied to the mortality rate, fertility rate and net migration separately, based on the assumption that they behave independently. Therefore, to fit the model to historical fertility rates, let $y_t(x)$ in equation \eqref{eq:HU_1} denote the observed historical fertility data. However, for mortality rate by sex, the product-ratio method is used to ensure the forecast of females and males are non-divergent or coherent [@HBY13]. In the product-ratio method, after smoothing the female and male mortality rates, two other series were created: product series (denoted by $p_t(x)$) and ratio series (denoted by $r_t(x)$), which are defined as follows:
\begin{align}
  p_t(x)&=\sqrt{s_{t,M}(x)s_{t,F}(x)}, \label{eq:coherent_1}\\
  r_t(x)&=\sqrt{\frac{s_{t,M}(x)}{s_{t,F}(x)}}. \label{eq:coherent_2}
\end{align}
Then, @HU07 was applied to these two new variables instead of male and female mortality rate as follows:
\begin{align*}
  \ln[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
  \ln[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
\end{align*}
where time series $\left\{\beta_{t,j}\right\}$ are fitted with an ARIMA model while $\left\{\gamma_{t,l}\right\}$ are fitted by stationary ARFIMA model (i.e., $d$ in ARIMA($p,d,q$) constrained to $0<d<\frac{1}{2}$). It is the stationary constraint on $\gamma_{t,l}$ that ensures the forecast of male and female do not diverge. Then, simulation h-step-ahead forecast values of product variable and ratio variable was performed (denoted by $p_{n+h\mid n}(x)$ and $r_{n+h\mid n}(x)$ respectively) according to \eqref{eq:coherent_1} and \eqref{eq:coherent_2}. From here, obtaining h-step-ahead forecast of sex-specific coherent mortality rates (denoted $m_{n+h\mid n,M}(x)$ and $m_{n+h\mid n,F}(x)$) was performed using a back-transformation:
\begin{align*}
  m_{n+h\mid n,M}(x) & = p_{n+h\mid n}(x)r_{n+h\mid n}(x)\\
  m_{n+h\mid n,F}(x) & = p_{n+h\mid n}(x)/r_{n+h\mid n}(x)
\end{align*}
The method for simulating $h$-step-ahead values of net migration by sex is similar to the above method used on mortality rates except no log scale is applied to net migration. A stationary constraint was imposed on the ARIMA model for net migration to make sure the difference between sexes did not diverge.

@@

Even though the OADR is a simple function of the population age structure and pension age, the formula can't be directly applied to the simulated population array because the pension age changes over time. To overcome this problem, we assume that the pension age can only be adjusted at the beginning of a year for these calculations. Therefore, one pension age is applicable for a whole year and hence OADR is generated at the beginning of each year to show the trend. We will show the process of obtaining a one-step-ahead OADR (i.e., forecast of OADR in year 2011), given a specific pension age. The same method can be applied to all years over the prediction horizon, given their corresponding pension age. Further, the fractional pension age causes practical issues in calculating OADR, since ages are recorded as integers. We will also show how this issue was handled in the example below.

Suppose the pension age for $n+1$ is $a.r$ where $a$ is the integer and and $r$ is the reminder of pension age. Recall that for $h=1$, we can express the simulated population paths as a matrix with age in the row and simulation in the column as follows:
\begin{equation*}
  \bm{p}_{n+1}=[p_{m,i}] =
    \begin{bmatrix}
       p_{1,1} & \cdots\cdots & p_{1,1000} \\
      \vdots & \ddots & \vdots \\
      p_{100^+,1} & \cdots\cdots &p_{100^+,1000}
      \end{bmatrix}.
\end{equation*}
When $r=0$, then the simulation of a population aged 15 to pension age is a subset of the above matrix from $15^{th}$ row to $a-1^{th}$ row, which is:
\begin{equation}
  \begin{bmatrix}
    p_{15,1} & \cdots\cdots & p_{15,1000} \\
    \vdots & \ddots & \vdots \\
    p_{a-1,1} & \cdots\cdots &p_{a-1,1000}
  \end{bmatrix}. \label{eq:population_mat}
\end{equation}
To calculate the total number of working age, we take a column sum of the trimmed matrix \eqref{eq:population_mat}. The simulations of total number of work age become a vector:
\begin{equation}
  \bm{p}^{\text{work}}_{n+1} = \left[\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}\right] \label{eq:work}
\end{equation}
Using the same method, the simulations of total number of aged pensioners in the population can be shown as:
\begin{equation}
  \bm{p}^{\text{aged}}_{n+1} = \left[\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}\right]\label{eq:aged}
\end{equation}

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = TRUE)
# Make sure you have the latest version of rmarkdown and bookdown
# devtools::install_github("rstudio/rmarkdown")
# devtools::install_github("rstudio/bookdown")
# And the latest versions of Our packages
# devtools::install_github("robjhyndman/forecast")
# devtools::install_github("robjhyndman/demography")
# devtools::install_github("robjhyndman/addb")
library(demography)
library(addb)
library(ggplot2)
library(kableExtra)
source("functions-v4.R")
```

@@

```{r changespension, echo=FALSE, fig.cap="Government's adjustments on pension age scheme.", fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
year <- 2057 - 2007
proposed <- ts(pmin(
  70,
  c(rep(65, 2017 - 2008), 65 + cumsum(rep(c(0.5, 0), 55)))
)[1:50],
start = 2008
)
approved <- pmin(proposed, 67)
current <- pmin(proposed, 65)
cols <- c(current = "#1b9e77", approved = "#d95f02", proposed = "#7570b3")
ggplot() +
  forecast::autolayer(proposed, series = "proposed") +
  forecast::autolayer(approved, series = "approved") +
  forecast::autolayer(current, series = "current") +
  xlab("Year") + ylab("Age of retirement") +
  scale_color_manual(
    values = cols, name = " ",
    breaks = c("current", "approved", "proposed"),
    labels = c("Pension age at 65", "Approved change", "Proposed further change")
  )
```

@@

The model proposed by @LC92 is as follows:
\begin{equation}
  \ln(m_{x,t})=a_x+b_xk_t+\epsilon_{x,t}
\end{equation}
where $m_{x,t}$ is the central death rate\footnote{The central death rate is properly defined in Section~\ref{sec:data}} for age $x$ in year $t$. This model involves fitting a matrix of log central death rates with sets of age-specific constants, {$a_x$} and {$b_x$}, and a time-varying index $k_t$. $b_x$ is a set of parameters that tell us the rate at which each age responds to changes in $k_t$. $k_t$ measures the general level of the log death rates; $a_x$ is the general pattern across age of the log mortality rate and $\epsilon_{x,t}$ is an error term with zero mean and constant variance, reflecting the randomness that can't be captured by the model.

The model is under-determined in terms of estimation of parameters. For example, if the vector $a,b,k$ is one solution, then for any scalar $c$, $a, b/c, kc$ or $a - bc, b, k+c$ also must be two possible solutions. Therefore, Lee and Carter (1992) impose the following constraints:
\begin{equation}
  \sum_{t=1}^{n}k_t=0, \qquad \sum_{x=x_1}^{x_m}b_x=1
\end{equation}
Also, we normally seek the least squares solution when estimating parameters. However, in this case, the model cannot be estimated using simple regression methods because there is no regressor on the right side of the equation. @LC92 choose a singular value decomposition (SVD) method to undertake principal component analysis (PCA), and hence find the least squares solution. It has been shown that applying SVD method to a matrix of the logarithms of the rates after subtracting the average over time of the log age-specific rates can find the least square solution (Good, 1969). Therefore, the estimations of $b_x$ and $k_t$ are the first principal component and scores of $\ln(m_{x,t})-a_x$ (i.e., $b_x=\bm{z_1}$ and $k_t=\bm{u_1}'$  when $\bm{X}=\ln(m_{x,t})-a_x$). However, the empirical results suggest that the resulting fitted number of deaths are biased estimates of actual number of deaths because of the $\ln$ transformation. To overcome this problem, the LC method adjusts $k_t$ such that for each year, the implied number of deaths will be equal to the actual number of deaths. The adjusted $k_t$ is then extrapolated using random walk with drift models, which is equivalent to ARIMA ($0,1,0$) model with $c\neq0$.

### Hyndman-Ullah Method \label{sec:HU}

@@

The model proposed by @HU07 is as follows:
\vspace{-.3in}
\begin{align}
  y_t(x) & = s_t(x) + \sigma_t(x)\epsilon_{t,x}\label{eq:HU_1}\\
  s_t(x) & = \mu(x) + \sum_{j=1}^{J}\beta_{t,j}\phi_j(x) + e_t(x)\label{eq:HU_2}
\end{align}
Equation \eqref{eq:HU_1} describes the smoothing process. $y_t(x)$ is the observed data in year $t$ and age $x$, and $s_t(x)$ is the smoothed function of $y_t(x)$, estimated by constrained weighted penalized regression splines [@BHT14]. $\sigma_t(x)$ allows the variance to be a function of time and age; and $\epsilon_{t,x}$ are independent identical distributed standard normal error terms. Equation \eqref{eq:HU_2} has a similar structure to the LC method, except that it incorporates more than one principal component and score. It describes the dynamics of $s_t(x)$ over time. The $\beta_{t,j}$ for every $j$ and $\mu(x)$ are sets of age-specific constants, and $\phi_j(x)$ for every $j$ is a time-varying index. The $e_t(x)$ is the model error, which is the residual function with mean zero and no serial correlation. The $\mu(x)$ is estimated by the average of $s_t(x)$ across years, which measures the general shape of the observed data $y_t(x)$. The estimates of $\phi_j(x)$ and $\beta_{t,j}$ are the $j$th principal component and scores of $s_t(x)-\mu(x)$ respectively. In other words, we take singular value decomposition of $s_t(x)-\mu(x)$, then \eqref{eq:HU_2} now becomes
\vspace{-.2in}
\begin{equation*}
  s_t(x)-\mu(x) = \phi_1(x)\beta_{t,1}+\phi_2(x)\beta_{t,2}+\dots+\phi_J(x)\beta_{t,J}
\end{equation*}
We chose $J$ in a way that we believe the majority of information for $s_t(x)-\mu(x)$ has been captured by the first $J$ components.

In terms of forecasting, by conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}$ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of log rate $y_{n+h}(x)$ can be acquired by:
\vspace{-.2in}
\begin{equation}
  \widehat{y}_{n+h\mid n}(x)=\widehat{s}_{n+h\mid n}(x) = \text{E}[\widehat{s}_{n+h\mid n}(x)\mid \bm{I, B}] = \widehat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\widehat{\beta}_{n+h\mid n,j}
\end{equation}
where $\widehat{\beta}_{n+h\mid n,j}$ denotes the $h$-step-ahead forecast of $\beta_{n+h\mid n,j}$. Because of the time-varying property of $\left\{\beta_{t,j}\right\}$, it controls the dynamics of the process. For every component series $\left\{\beta_{t,j}\right\}$, we fit them with an ARIMA$(p_j,d_j,q_j)$ process, where $p_j,d_j,q_j$ are determined by minimizing the Akaike Information Criterion (Booth, Hyndman \& Tickle, 2014). The fitted process is given as follows:
\vspace{-.3in}
\begin{equation*}
  (1-\phi_1B-\dots-\phi_{p_j}B^{p_j})(1-B)^{d_j}\beta_{t,j}=c+(1+\theta_1B+\dots+\theta_{q_j}B^{q_j})e_t, \quad ~\forall j=1,2,\dots,J,
\end{equation*}
where the parameters are estimated using maximum likelihood estimation.

@@

We use the same notation and similar procedures to construct data as in @HB08, because the fundamental model for forecasting population for this study is the @HU07 method. The data used to construct population age structure included: age- and gender-specific birth and death numbers of each calendar year, age- and gender-specific population members on 1\ January of each year, and age- and gender-specific exposures to risk (i.e., population of age $x$ at 30 June) for each year. The notations are as follows:
\vspace{-.4in}
\begin{align*}
  B_t(x) &= \text{Births in calendar year $t$ to females of age $x$}\\
  D_t(x) &= \text{Deaths in calendar year $t$ of persons of age $x$}\\
  P_t(x) &= \text{Population of age $x$ at 1 January of year $t$}\\
  E_t(x) &= \text{Population of age $x$ exposed to risk at 30 June of year $t$}\\
\end{align*}
\vspace{-.4in}where $x$ denotes age and $x=0,1,2,\dots,m^+$. $m^+$ is the open-ended upper age group, which is 100 in this study. $t$ denotes year and $t=1,2,\dots,n$, where $n$ is the horizon of historical data used. Therefore, all of those data points can be recorded in an $m\times n$ matrix.  The superscripts M and F denote male and female respectively.

We can obtain historical mortality rates $m_t(x)$ (also called central death rates) and fertility rates $f_t(x)$ as follows:
\vspace{-.3in}
\begin{align*}
  m_t(x) & = \frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year t}\\
  f_t(x) & = \frac{B_t(x)}{E^F_t(x)}=\text{age-specific fertility rates in calendar year t}
\end{align*}

In addition, the net migration\footnote{Net migration is the difference between immigration and emigration in a certain area during a specified time frame} (denoted $G$) is estimated using a demographic growth-balance equation, which is an equation to summarize the relationship between population change and three factors: net migration, births and deaths. The equation is expressed as: \todo{Please define $p$ and $^+$}
\vspace{-.3in}
\begin{align*}
  G_t(x,x+1)     & =P_{t+1}(x+1)-P_t(x)+D_t(x,x+1)\text{~for~} x=0,1,2,\dots,p-2,\\
  G_t(p-1^+,p^+) & =P_{t+1}(p^+)-P_t(p^+)-P_t(p-1)+D_t(p-1^+,p^+)\\
  G_t(B,0)       & =P_{t+1}(0)-B_t+D_t(B,0)
\end{align*}
where $G_t(x,x+1)$ refers to net migration in calendar year $t$ of persons aged $x$ at beginning of year $t$, $G_t(p-1^+,p)$ \todo{should it be $p^+$} refers to migration in calendar year $t$ of persons aged $p-1$ and older at beginning of year $t$, and $G_t(B,0)$ refers to deaths in calendar year $t$ of births during year $t$; and similarly for deaths, $D_t(x,x+1), D_t(p-1^+,p^+), D_t(B,0)$. The deaths are estimated using the standard life table approach of population projection. It should be noted that the estimated net migration includes errors in data recording.

Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0-99 and 100+ have been sourced from the @HMD for 1921--2014.\todo{Han has updated the data period.} The start-year population for 2015 is also used to estimate net migration. Data for age-specific annual fertility rates by single years of age for 15-49 over the period 1950-2014 was obtained from the @ABS12. Even though annual mortality rates are available from 1921 to 2014, only data collected after 1950 is used for two reasons. First, the period between 1921-1950 has very different mortality patterns from later years because of wars and epidemics [@HB08]. Since the model for this study is valid under the assumption that extrapolative methods can be used, it seemed best to delete the less relevant data, which might influence estimations of parameters if we include them. Secondly, fertility rates are only available from 1950, so the mortality rate was cut to fit the same period.

@@

In this study, three steps were taken to simulate OADR associated with a specific pension age scheme. A stochastic functional data model was applied to five components of population change: female mortality rates, male mortality rates, female net migration, male net migration and fertility rates to simulate these five components over the prediction horizon (which is 50 years in this study). Age- and gender-specific population paths over the prediction horizon were simulated using the demographic growth-balance equation. The Monte Carlo simulation method was used consistently in this research. Finally, calculation of OADR associated with a specific pension age scheme was performed by applying the OADR formula. Even though the process seems complicated, it is relatively resy to implement using \textit{R} [@Team18]. The detailed explanation of each step is as follows. The corresponding R code is attached as a supplement.

@@

The main procedure for forecasting the population age structure follows @HB08, except that the data is updated, and we incorporate the product-ratio method [@HBY13] to improve the accuracy of the forecast. The @HU07 model, introduced in section \ref{sec:HU}, is applied to the mortality rate, fertility rate and net migration separately, based on the assumption that they behave independently. Therefore, to fit the model to historical fertility rates, let $y_t(x)$ in equation \eqref{eq:HU_1} denote the observed historical fertility data. However, for mortality rate by sex, the product-ratio method is used to ensure the forecast of females and males are non-divergent or coherent [@HBY13]. In the product-ratio method, after smoothing the female and male mortality rates, two other series were created: product series (denoted by $p_t(x)$) and ratio series (denoted by $r_t(x)$), which are defined as follows:
\vspace{-.4in}
\begin{align}
  p_t(x)&=\sqrt{s_{t}^{\text{M}}(x)s_{t}^{\text{F}}(x)}, \label{eq:coherent_1}\\
  r_t(x)&=\sqrt{\frac{s_{t}^{\text{M}}(x)}{s_{t}^{\text{F}}(x)}}. \label{eq:coherent_2}
\end{align}
Then, @HU07 was applied to these two new variables instead of male and female mortality rate as follows:
\vspace{-.3in}
\begin{align*}
  \ln[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
  \ln[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
\end{align*}
where time series $\left\{\beta_{t,j}\right\}$ are fitted with an ARIMA model while $\left\{\gamma_{t,l}\right\}$ are fitted by stationary ARFIMA model (i.e., $d$ in ARIMA($p,d,q$) constrained to $0<d<\frac{1}{2}$). It is the stationary constraint on $\gamma_{t,l}$ that ensures the forecast of male and female do not diverge. Then, simulating $h$-step-ahead forecast values of product variable and ratio variable was performed (denoted by $p_{n+h\mid n}(x)$ and $r_{n+h\mid n}(x)$ respectively) according to \eqref{eq:coherent_1} and \eqref{eq:coherent_2}. From here, obtaining $h$-step-ahead forecast of sex-specific coherent mortality rates (denoted $m_{n+h\mid n,M}(x)$ and $m_{n+h\mid n,F}(x)$) was performed using a back-transformation:
\vspace{-.3in}
\begin{align*}
  m_{n+h\mid n}^{\text{M}}(x) & = p_{n+h\mid n}(x)r_{n+h\mid n}(x)\\
  m_{n+h\mid n}^{\text{F}}(x) & = p_{n+h\mid n}(x)/r_{n+h\mid n}(x)
\end{align*}
The method for simulating $h$-step-ahead values of net migration by sex is similar to the above method used on mortality rates except no log scale is applied to net migration. A stationary constraint was imposed on the ARIMA model for net migration to make sure the difference between sexes did not diverge.

@@

Even though the OADR is a simple function of the population age structure and pension age, the formula can't be directly applied to the simulated population array because the pension age changes over time. To overcome this problem, we assume that the pension age can only be adjusted at the beginning of a year for these calculations. Therefore, one pension age is applicable for a whole year and hence OADR is generated at the beginning of each year to show the trend. We will show the process of obtaining a one-step-ahead OADR (i.e., forecast of OADR in year 2015), given a specific pension age. The same method can be applied to all years over the prediction horizon, given their corresponding pension age. Further, the fractional pension age causes practical issues in calculating OADR, since ages are recorded as integers. We will also show how this issue was handled in the example below.

Suppose the pension age for $n+1$ is $a.r$ where $a$ is the integer and and $r$ is the reminder of pension age. Recall that for $h=1$, we can express the simulated population paths as a matrix with age in the row and simulation in the column as follows:
\begin{equation*}
  \bm{p}_{n+1}=[p_{n+1,m,i}] =
    \begin{bmatrix}
       p_{1,1} & \cdots\cdots & p_{1,1000} \\
      \vdots & \ddots & \vdots \\
      p_{100^+,1} & \cdots\cdots &p_{100^+,1000}
      \end{bmatrix}.
\end{equation*}
When $r=0$, then the simulation of a population aged 15 to pension age is a subset of the above matrix from $15^{th}$ row to $a-1^{th}$ row, which is:
\begin{equation}
  \begin{bmatrix}
    p_{15,1} & \cdots\cdots & p_{15,1000} \\
    \vdots & \ddots & \vdots \\
    p_{a-1,1} & \cdots\cdots &p_{a-1,1000}
  \end{bmatrix}. \label{eq:population_mat}
\end{equation}
To calculate the total number of working age, we take a column sum of the trimmed matrix \eqref{eq:population_mat}. The simulations of total number of work age become a vector:
\begin{equation}
  \bm{p}^{\text{work}}_{n+1} = \left[\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}\right] \label{eq:work}
\end{equation}
Using the same method, the simulations of total number of aged pensioners in the population can be shown as:
\begin{equation}
  \bm{p}^{\text{aged}}_{n+1} = \left[\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}\right]\label{eq:aged}
\end{equation}

When $r\neq0$, the vector of total number of working age population in \eqref{eq:work} is added, and the vector of total number of aged population in \eqref{eq:aged} is subtracted with an adjustment:
\vspace{-.2in}
\begin{equation}
  \text{adjustment}=0.r\times100\%[p_{a,1},p_{a,2},\dots,p_{a,1000}]
\end{equation}
This adjustment is based on the assumption that the birthday of population is uniformly distributed over the year. Then, $r\times100\%$ of population with a recorded integer age of $a$ at beginning of the year is actually younger than $a.r$, so they are still under the pension age. In other words, $(1-r\times100\%)$ of population with recorded integer age $a$ at beginning of the year is actually older than $a.r$, so they should be counted as the aged population. The simulation vectors of total work age population and total aged population should then be: 
\begin{align*}
  \bm{p}^{\text{work}}_{n+1}
    & = \left[p^{\text{work}}_{n+1,1},p^{\text{work}}_{n+1,2},\dots,p^{\text{work}}_{n+1,1000}\right]\\
    & = \left[\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}\right]+0.r\times100\%\left[p_{a,1},p_{a,2},\dots,p_{a,1000}\right]   \\
  \bm{p}^{\text{aged}}_{n+1}
    & = \left[p^{\text{aged}}_{n+1,1},p^{\text{aged}}_{n+1,2},\dots,p^{\text{aged}}_{n+1,1000}\right]\\
    & = \left[\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}\right]-0.r\times100\%\left[p_{a,1},p_{a,2},\dots,p_{a,1000}\right]
\end{align*}
